Agreement Attraction in Turkish: The Case of Genitive Attractors\\ \bigskip \large Word count: 3303

### 2021-11-06 paper/glossa/manuscript-knitr.Rnw
osf2

In the results section, we provide summaries of the coefficient posterior distributions. For our model, we ran \Sexpr{n_chains} chains with \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations. The data for our study, along with our analysis scripts can be found \url{hhttps://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}.

@@

The data that support the findings of this study, the code, and the paper resources including \LaTeX{} and \texttt{Sweave} files are openly available in the anonimized github page at \url{https://anonymous.4open.science/r/tr_short_agreement_attraction-1365/}. %exclude

>>>>

In the results section, we provide summaries of the coefficient posterior distributions. For our model, we ran \Sexpr{n_chains} chains with \Sexpr{n_warmup} warm-up iterations and \Sexpr{n_iter-n_warmup} sampling iterations. The data for our study, along with our analysis scripts can be found \url{https://osf.io/hegmd/}.

@@

All data and R code used in the data analysis is available at \url{https://osf.io/hegmd/}. %exclude
